Sparse Word Embedding for Multi-domain Machine Translation

### 2019-04-18 2019/emnlp/sparse.tex
new

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2019}
\usepackage{times}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{url}
\usepackage{float} 
\usepackage{tabularx}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{definition}{Definition}[section]
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\usepackage{algorithm}
\usepackage{algorithmic}
\floatname{algorithm}{Procedure}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\section{Introduction}
Despite fast developpemnt thanks to new architectures \cite{NIPS2017_7181} \cite{bahdanau2014neural} \cite{D13-1176} \cite{Sutskever2014Sequence}, Machine Translation still struggles with data scarcity. Domain adaptation, or it's special case Multi-domain, is the situation where in-domain data (such as banking) is rare while out-domain data such as news are plenty, one aims to leverage out-domain data to improve quality of Machine Translation system which is perfectible while being trained with only the in-domain dataset. Traditionally, ones train a generic model using a very large corpora then use in-domain dataset to finetune the model. It is ubiquitous that the bias to the in-domain dataset used in finetuning makes model worse in translating other domains, thus that we have not been able to finetune a model to several domains at once. This phenomenon can be implied by well-known problem in Machine Learning, Catastrophic Interference \cite{Michael1989Catastrophic}. When there is a shift in the distribution of training data, standard backpropagation neural network gradually lose information learned from other domains while learning only target domain.\\
In Multi-domain Machine Translation, ones have to deal with polysemies whose meaning can be totally different in different domains, for example, the word "chair" means an household tool in "if you are taking a medicine which may cause low blood pressure when rising from a chair or bed " (extracted from medical corpora EMEA \cite{Tiedemann2009RANLP5}) while the word "chair" means to preside over a meeting in following sentence "The President of the ECB or , in his absence , the Vice-President , chairs the meetings of the Governing Council , the Executive Board and the General Council of the ECB. " (extracted from European Central Bank corpora \cite{Tiedemann2009RANLP5}). Using context information is not sufficient to differ these polysemies. Therefore using the same word embedding for polysemies obstructs the model from differentiating the meaning of a polysemy in one domain from it's other meaning in the other domain. \\
\begin{table}[h]
\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|l|}
\hline
English Words & French translation & Domain \\ \hline
security & titre financier & Financial \\
security & s\'ecuti\'e & IT\\
joint & articulaire & medical\\
joint & conjoint & banking\\
chair & chaise & general \\
chair & pr\'esider, pr\'esident & banking \\
\hline
\end{tabular}
}
\caption{Polysemies}
\label{table:polysemy}
\end{table}

\begin{table}[h]
\resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||}
\hline
English sentence & French translation & Domain \\ 
\hline
"Flu-like" symptoms such as headaches, joint pains, feelings of weakness, dizziness, and tiredness may occur, especially at the start of treatment. & Des symptômes grippaux tels que céphalées, douleurs articulaires, sensation de faiblesse, vertige et asthénie, peuvent survenir, en particulier en début de traitement. & medical \\
\hline
\end{tabularx}
}
\caption{Polysemies}
\label{table:polysemy}
\end{table}

In this work, we present a new design for word embedding that is composed of different regions which are activate and deactivate corresponding to domains. To evaluate, we use several test sets representing each domains and two other general test sets.
\section{Related Work}
Multi-domain Machine Translation has largely interested NLP community by its promising applications in industry and its relation to fundamental problems in theory. Researchers have proposed a large range of techniques from Data centric methods to Model centric methods \cite{C18-1111}; \cite{P17-2061}. Data centric methods have goal to collect related-domain data from existing in-domain data by using different techniques such as scoring relatedness by Language Model \cite{P10-2041}; \cite{D11-1033}; \cite{P13-2119} or by metric on the space of sentence embedding \cite{P17-2089} or generating pseudo parallel data \cite{P03-1010}; \cite{C16-1295}; \cite{D14-1023}. On the other hand, Model centric approaches focus on NMT models that are specialized for domain adaptation. The novelty can be either trainining objective; for example \cite{Luong2015SNMT}; \cite{P16-1009}; \cite{D17-1155}; \cite{W17-3205}; \cite{D17-1156}; \cite{C18-1269} or architecture \cite{R17-1049}; \cite{gulcehre2016monolingual}; \cite{W17-4712}, \cite{Biao2017CARENMT}; \cite{N18-2080}; \cite{W18-6313}; \cite{C16-1170}; \cite{P18-2050} or the decoding algorithm \cite{gulcehre2016monolingual}; \cite{I17-2004}. Beside these works, we could also consider "out-of-domain" works such as sequence labeling tasks \cite{P07-1033}; learning multiple visual domains \cite{NIPS2017_6654}. The problem is recently investigated by several interesting works presented in EMNLP 2018 such as \cite{D18-1039}; \cite{D18-1041}. \cite{D18-1041} create in the encoder Domain-specific gate $g^r_i$and Domain-shared gate $g^s_i$ which are generated from domain-specific and domain-shared semantic representations of source sentence $E_r(x)$ and $E_s(x)$ respectively and which select information from units of hidden states $h_i$ by elementwise product $h^r_i = g^r_i \odot h_i$; $h^s_i = g^s_i \odot h_i$. $h^r_i$ and $h^s_i$ will be fed to Domain-specific and Domain-shared attentional mechanisms respectively. While introducing new features in the architecture, \cite{D18-1041} introduces also new objective which is sum of word-level weighted MT objective and objectives of Domain-classifier in source side and target side and Adversarial Domain-classifier in source side. The author have very good approach to well seperate Domain-shared information flow and Domain-specify information flow and determine their contributions to the inference that mitigates the catastrophic interference happens in the network during forward step.

\section{Proposed method}
\subsection{Problem statement}
\begin{definition}{Domain}
\label{def:1}
Domain is a hypothetical probability that generates a set of corpora. We will denote D(C) is domain of set of corpora C.
\end{definition}

@@

@@

Denote $p_{t} = P * w_{t}$ where $w_{t}$ is word embedding of token $x_{t}$  is projection of word embedding (Transformer \cite{NIPS2017_7181}, Recurrent \cite{bahdanau2014neural})

@@

Furthermore, because word embeddings are involved in three parts of standard encoder-decoder structure, which are input of encoder, input of decoder and projection before softmax, we have 7 possibilities to apply sparse embedding. However, due to high memory cost, we only want to apply sparse embedding in encoder.

@@

Each iteration of algorithm \ref{algo:1}, the batch is doubled because it contains 2 types of word embedding for each sentence (using only generic region; using generic region and active domain region). The reason to do this is to minimize simultaneously both losses \\
$\theta^*_{s} = \displaystyle{\mathop{\argmin}_{\theta_s}}E_{(x,y) \sim D(\displaystyle{\mathop{\cup}_{i \in [1,..,d]}}C_{i})}[-log(p_{\theta_s}(y|x))]$ \\ 
$ \theta^*_{i} =\displaystyle{\mathop{\argmin}_{\theta_i}}E_{(x,y) \sim D(C_{i})}[-log(p_{\theta_i,\theta^*_s}(y|x,i))]
$ 
We admit that this is not the optimal way. However, this procdedure make the training very simple.\\
We also take in account the problem of overfitting that could occur for small corpora. Indeed, real data are not always balanced for every domain. For instance, in our experiments, the size of corpora are very different where EPPS is largest with approximately 2 millions sentences, EMEA contains about 1 million sentences and ECB is the smallest with only 200 000 sentences for English French and 100 000 for English German. If we train each corpora with same number of batches, ECB will be trained too oftenly, that easily leads to overfitting. Therefore, we perform backpropagation on corpora with frequencies according to sizes of corpora.
\subsection{Results}
\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 67.69 & 37.5 & 53.49 & 34.86 & 30.96 & 20.98 & 25.7 \\
 \hline
 EMEA-finetuned & 76.77 & 17.16 & 11.99 & 29.58 & 14.25 & 9.92 & 11.10 \\
 \hline
 EPPS-finetuned & 20.86 & 37.04 & 24.53 & 31.86 & 30.97 & 20.72 & 11.1 \\
 \hline
 ECB-finetuned & 9.2 & 18.39 & 55.45 & 12.13 & 16.12 & 8.71 & 7.19 \\
 \hline
 Sparse(1) & 70.45 & 38.23 & 54.69 & 34.66 & 31.24 & 21.36 & 26.02 \\
 \hline
 Sparse(2) & 69.91 & 38.05 & 54.2 & 35.22 & 31.25 & 21.36 & 26.02 \\
 \hline
 Sparse(3) &  &  &  &  &  &  & \\
 \hline
 Domain Control & 67.87 & 37.31 & 54.14 & 33.63 & 31.09 & & \\
 \hline
\end{tabularx}}
\end{center}
\caption{bpe-detokenized BLEU score in language pair English - French. Sparse(1) uses correponding domain tag for EMEA, EPPS, ECB test sets and generic tag for newstest and IWSLT. Sparse(2) uses generic tag for all of test sets. Sparse(3) uses tag predicted by pretrained domain classififer}
\label{tab:1}
\end{figure}

\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & & & & & & & \\
 \hline
 EMEA-finetuned & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & \\
 \hline
 Sparse & & & & & & & \\
 \hline
 Domain Control & & & & & & & \\
 \hline
\end{tabularx}}
\end{center}
\caption{BLEU score for Transformer in language pair English - German. The notation is same as \ref{tab:1}}
\label{tab:2}
\end{figure}

\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 67.69 & 37.5 & 53.49 & 34.86 & 30.96 & 20.98 & 25.7 \\
 \hline
 EMEA-finetuned & 76.77 & 17.16 & 11.99 & 29.58 & 14.25 & 9.92 & 11.10 \\
 \hline
 EPPS-finetuned & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & \\
 \hline
 Sparse(1) & 70.45 & 38.23 & 54.69 & 34.66 & 31.24 & 21.36 & 26.02 \\
 \hline
 Sparse(2) & 69.91 & 38.05 & 54.2 & 35.22 & 31.25 & 21.36 & 26.02 \\
 \hline
 Sparse(3) &  &  &  &  &  &  & \\
 \hline
 Domain Control & 67.87 & 37.31 & 54.14 & 33.63 & 31.09 & & \\
 \hline
 WDCMT (conditional GRU) & & & & & & & \\
 \hline
\end{tabularx}}
\end{center}
\caption{bpe-detokenized BLEU score for Recurrent network architecture on language pair English-French. Notations as same as \ref{tab:1} except that other models from WDCMT of \cite{D18-1041} use Bidirectional-LTSM}
\label{tab:3}
\end{figure}

\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & & & & & & & \\
 \hline
 EMEA-finetuned & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & \\
 \hline
 Sparse & & & & & & & \\
 \hline
 Domain Control & & & & & & & \\
 \hline
 WDCMT (conditional GRU) & & & & & & & \\
 \hline 
\end{tabularx}}
\end{center}
\caption{BLEU score for Recurrent network on language pair English - German. The notation is same as \ref{tab:3}}
\label{tab:4}
\end{figure}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2019}
\usepackage{times}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{url}
\usepackage{float} 
\usepackage{tabularx}
\usepackage{xcolor}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{definition}{Definition}[section]
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\usepackage{algorithm}
\usepackage{algorithmic}
\floatname{algorithm}{Procedure}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\section{Introduction}
Despite fast developpemnt thanks to new architectures \cite{NIPS2017_7181} \cite{bahdanau2014neural} \cite{D13-1176} \cite{Sutskever2014Sequence}, Machine Translation still struggles with data scarcity. Domain adaptation, or it's special case Multi-domain, is the situation where in-domain data (such as banking) is rare while out-domain data such as news are plenty, one aims to leverage out-domain data to improve quality of Machine Translation system which is perfectible while being trained with only the in-domain dataset. Traditionally, ones train a generic model using a very large corpora then use in-domain dataset to finetune the model. It is ubiquitous that the bias to the in-domain dataset used in finetuning makes model worse in translating other domains, thus that we have not been able to finetune a model to several domains at once. This phenomenon can be implied by well-known problem in Machine Learning, Catastrophic Interference \cite{Michael1989Catastrophic}. When there is a shift in the distribution of training data, standard backpropagation neural network gradually lose information learned from other domains while learning only target domain.\\
In Multi-domain Machine Translation, ones have to deal with polysemies whose meaning can be totally different in different domains, for example, the word "chair" means an household tool in "if you are taking a medicine which may cause low blood pressure when rising from a chair or bed " (extracted from medical corpora EMEA \cite{Tiedemann2009RANLP5}) while the word "chair" means to preside over a meeting in following sentence "The President of the ECB or , in his absence , the Vice-President , chairs the meetings of the Governing Council , the Executive Board and the General Council of the ECB. " (extracted from European Central Bank corpora \cite{Tiedemann2009RANLP5}). Using context information is not sufficient to differ these polysemies. Therefore using the same word embedding for polysemies obstructs the model from differentiating the meaning of a polysemy in one domain from it's other meaning in the other domain. \\
\begin{table}[h]
\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|l|}
\hline
English Words & French translation & Domain \\ \hline
security & titre financier & Financial \\
security & s\'ecuti\'e & IT\\
\hline
joint & articulaire & medical\\
joint & conjoint & banking\\
\hline
chair & chaise & general \\
chair & pr\'esider, pr\'esident & banking \\
\hline
\end{tabular}
}
\caption{Polysemies}
\label{table:polysemy}
\end{table}

\begin{table}[h]
\resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||}
\hline
English sentence & French translation & Corpora \\ 
\hline
"Flu-like" symptoms such as headaches, \colorbox{red}{joint} pains, feelings of weakness, dizziness, and tiredness may occur, especially at the start of treatment. & Des symptômes grippaux tels que céphalées, douleurs \colorbox{red}{articulaires}, sensation de faiblesse, vertige et asthénie, peuvent survenir, en particulier en début de traitement. & EMEA \\
\hline
In my opinion, Mr President, this \colorbox{red}{joint} debate fully bears this out. & Cette discussion \colorbox{red}{commune} en est, Monsieur le Président, la preuve vivante. & EPPS \\
\hline
The increasing number of central banks using the same IT platform for their own purposes has provided unique opportunities to undertake \colorbox{red}{joint} projects , exploit synergies and better manage the relationship with the vendor. & Le nombre croissant de banques centrales utilisant la même plate-forme informatique pour leurs besoins propres a offert des occasions uniques de lancer des projets \colorbox{red}{communs}, d'exploiter des synergies et de mieux gérer les relations avec le fournisseur. & ECB \\
\hline
\end{tabularx}
}
\caption{Translation}
\label{table:polysemy}
\end{table}

In this work, we present a new design for word embedding that is composed of different regions which are activate and deactivate corresponding to domains. To evaluate, we use several test sets representing each domains and two other general test sets.
\section{Related Work}
Multi-domain Machine Translation has largely interested NLP community by its promising applications in industry and its relation to fundamental problems in theory. Researchers have proposed a large range of techniques from Data centric methods to Model centric methods \cite{C18-1111}; \cite{P17-2061}.\\ Data centric category attempts to collect related-domain data from large existing in-domain corpora. The methods in this category can be listed as following:
\begin{itemize}
	\item score relatedness of sentences to the target domain by Language Model \cite{P10-2041}; \cite{D11-1033}; \cite{P13-2119}.
	\item generating pseudo parallel data \cite{P03-1010}; \cite{C16-1295}; \cite{D14-1023}
\end{itemize}
On the other hand, Model centric approaches focus on NMT models that are specialized for domain adaptation. The novelty can be among following features
\begin{itemize}
	\item Trainining objective \cite{Luong2015SNMT}; \cite{P16-1009}; \cite{D17-1155}; \cite{W17-3205}; \cite{D17-1156}; \cite{C18-1269}
	\item Architecture \cite{R17-1049}; \cite{gulcehre2016monolingual}; \cite{W17-4712}, \cite{Biao2017CARENMT}; \cite{N18-2080}; \cite{W18-6313}; \cite{C16-1170}; \cite{P18-2050}.
	\item The decoding algorithm \cite{gulcehre2016monolingual}. \cite{I17-2004}
\end{itemize} 
Beside these works, we could also consider works in other tasks such as sequence labeling tasks \cite{P07-1033}; learning multiple visual domains \cite{NIPS2017_6654}. The problem is recently investigated by several interesting works presented in EMNLP 2018 such as \cite{D18-1039}; \cite{D18-1041}. \cite{D18-1041} create in the encoder Domain-specific gate $g^r_i$and Domain-shared gate $g^s_i$ which are generated from domain-specific and domain-shared semantic representations of source sentence $E_r(x)$ and $E_s(x)$ respectively and which select information from units of hidden states $h_i$ by elementwise product $h^r_i = g^r_i \odot h_i$; $h^s_i = g^s_i \odot h_i$. $h^r_i$ and $h^s_i$ will be fed to Domain-specific and Domain-shared attentional mechanisms respectively. While introducing new features in the architecture, \cite{D18-1041} also introduces new loss function which is sum of word-level weighted MT loss and losses of Domain-classifier in source side and target side; Adversarial Domain-classifier in source side. The authors have very good approach to seperate Domain-shared information flow and Domain-specify information flow and to determine their contributions to the inference thus mitigate the catastrophic interference occuring in training with backpropagation. \cite{D18-1039} has other idea to circumvent the catastrophic interference. They supposed that parameters of each domain specialized model could be generated from a universal parameter-generator. By introducing domain embedding (or Language embedding in the original paper), they could conduct domain related error in backpropagation toward domain embedding thus mitigates catastrophic interference between domains during training.\\
Compared to \cite{D18-1039}, our sparse embedding is a bit similar to the idea. However, our method gives much more free degree for domain embedding since we give each word a domain region while the author uses only one vector domain embedding for each parameter set(encoder, decoder).\\
Compared to the work of \cite{D18-1041}, our approach is much simpler and
more generic since sparse embedding can be implemented for every Neural architecture while Domain-specific gate and Domain-shared gate are applied only for Recurrent architectures. However, in the inference, the model of \cite{D18-1041} can infer the domain the closest to input sentence that will be used in special gates while our method need to know in which domain the inference is executed. To circumvent this disadvantage, we could use a domain classifier or simply use only generic region. For more detail, the reader could refer to the section \ref{sec:sparse}
\section{Proposed method}
\subsection{Problem statement}
\begin{definition}{Domain}
\label{def:1}
Domain is a hypothetical probability that generates a set of corpora. We will denote D(C) is domain of set of corpora C.
\end{definition}

@@

\label{sec:sparse}

@@

Denote \\
$p_{t} = P * w_{t} = P_g \omega_g(t) + \displaystyle{\mathop{\sum}_{i \in [1,..,d]} P_i * \omega_i(t)}$\\
where $w_{t}$ is word embedding of token $x_{t}$  is projection of word embedding (Transformer \cite{NIPS2017_7181}, Recurrent \cite{bahdanau2014neural})

@@

Furthermore, because word embeddings are involved in three parts of standard encoder-decoder structure, which are input of encoder, input of decoder and projection before softmax, we have 7 possibilities to apply sparse embedding. However, due to high memory cost, we only want to apply sparse embedding in source side.

@@

Each iteration of algorithm \ref{algo:1}, the batch is doubled because it contains 2 types of word embedding for each sentence (using only generic region; using generic region and active domain region). The reason to do this is to minimize simultaneously both losses \\
$\theta^*_{s}=\displaystyle{\mathop{\argmin}_{\theta_s}}E_{(x,y) \sim D(\displaystyle{\mathop{\cup}_{i \in [1,..,d]}}C_{i})}[-log(p_{\theta_s}(y|x))]$ \\ 
$ \theta^*_{i}=\displaystyle{\mathop{\argmin}_{\theta_i}}E_{(x,y) \sim D(C_{i})}[-log(p_{\theta_i,\theta^*_s}(y|x,i))]
$ 
We admit that this is not the optimal way. However, this procdedure make the training very simple.\\
We also take in account the problem of overfitting that could occur for small corpora. Indeed, real data are not always balanced for every domain. For instance, in our experiments, the size of corpora are very different where EPPS is largest with approximately 2 millions sentences, EMEA contains about 1 million sentences and ECB is the smallest with only 200 000 sentences for English French and 100 000 for English German. If we train each corpora with same number of batches, ECB will be trained too oftenly, that easily leads to overfitting. Therefore, we perform backpropagation on corpora with frequencies according to sizes of corpora.
\subsection{Results}
\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 67.69 & 37.5 & 53.49 & 34.86 & 30.96 & 20.98 & 25.7 \\
 \hline
 EMEA-finetuned & 76.77 & 17.16 & 11.99 & 29.58 & 14.25 & 9.92 & 11.10 \\
 \hline
 EPPS-finetuned & 20.86 & 37.04 & 24.53 & 31.86 & 30.97 & 20.72 & 11.1 \\
 \hline
 ECB-finetuned & 9.2 & 18.39 & 55.45 & 12.13 & 16.12 & 8.71 & 7.19 \\
 \hline
 Sparse(1) & 70.45 & 38.23 & 54.69 & 34.66 & 31.24 & 21.36 & 26.02 \\
 \hline
 Sparse(2) & 69.91 & 38.05 & 54.2 & 35.22 & 31.25 & 21.36 & 26.02 \\
 \hline
 Sparse(3) &  &  &  &  &  &  & \\
 \hline
 Domain Control & 67.87 & 37.31 & 54.14 & 33.63 & 31.09 & & \\
 \hline
\end{tabularx}}
\end{center}
\caption{bpe-detokenized BLEU score in language pair English - French. Sparse(1) uses correponding domain tag for EMEA, EPPS, ECB test sets and generic tag for newstest and IWSLT. Sparse(2) uses generic tag for all of test sets. Sparse(3) uses tag predicted by pretrained domain classififer}
\label{tab:1}
\end{figure}

\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & & & & & & & \\
 \hline
 EMEA-finetuned & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & \\
 \hline
 Sparse & & & & & & & \\
 \hline
 Domain Control & & & & & & & \\
 \hline
\end{tabularx}}
\end{center}
\caption{BLEU score for Transformer in language pair English - German. The notation is same as figure \ref{tab:1}}
\label{tab:2}
\end{figure}

\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 58.55 & 22.86 & 35.11 & 13.97 & 19.59 & 7.39 & 9.47 \\
 \hline
 EMEA-finetuned & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & \\
 \hline
 Sparse(1) & 58.45 & 23.22 & 35.98 & 13.66 & 19.5 & 7.63 & 10.39 \\
 \hline
 Sparse(2) & 56.18 & 23.05 & 35.16 & 15.95 & 20.08 & 7.63 & 10.39 \\
 \hline
 Sparse(3) &  &  &  &  &  &  & \\
 \hline
 Domain Control & 58.55 & 22.62 & 35.15 & 11.93 & 19.34 & & \\
 \hline
 WDCMT (conditional GRU) & & & & & & & \\
 \hline
\end{tabularx}}
\end{center}
\caption{bpe-detokenized BLEU score for Recurrent network architecture on language pair English-French. Notations as same as figure \ref{tab:1} except that other models from WDCMT of \cite{D18-1041} use Bidirectional-LTSM}
\label{tab:3}
\end{figure}

\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & & & & & & & \\
 \hline
 EMEA-finetuned & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & \\
 \hline
 Sparse & & & & & & & \\
 \hline
 Domain Control & & & & & & & \\
 \hline
 WDCMT (conditional GRU) & & & & & & & \\
 \hline 
\end{tabularx}}
\end{center}
\caption{BLEU score for Recurrent network on language pair English - German. The notation is same as figure \ref{tab:3}}
\label{tab:4}
\end{figure}
\subsection{Word embedding analysis}
